Toward a More Accessible and Reproducible ISLS Conference Proceedings Paper: A Practical Tutorial Using Cutting-Edge Tools

### 2021-01-12 paper_contents.tex
Add Expected outcomes and contributions

>>>>

\section{Expected outcomes and contributions}

The expected contributions of this tutorial is threefold. (1) Maintainability: the ISLS community will be able to have a manageable template archives that are easy-to-update and easy-to-distribute. The LaTeX-based template maintenance has become a widely-accepted standard in many computer science and HCI fields (e.g., ACM). Our proposal of using LaTeX template will not only push the ISLS community in a more universal direction across social sciences and computer science, but also contribute to general maintainability under a standardized typesettings. (2) Reproducibility: our computational word processing workflow will make it easy for learning scientists to transparently share and replicate analytical procedures. This will allow more reliable reviews and study results that would otherwise used to remain in a blackbox challenging against replicability. (3) Accessibility: the plain-text and multi-formatted nature of R Markdown workflow will greatly benefit the digital accessibility for people with and without (dis)abilities. Screen reader users will be able to easily navigate paper content (e.g., text, figures, tables, and even Math equations) in HTML output, and non-assistive-technology users will also take advantages of having multi-formatted outputs for various use following their own needs.

Taken together, this proposed tutorial will be the first step towards a more universal, reproducible, and accessible template management within ISLS community.
